\begin{textblock}{15.}(0., -5.)
    This slide lists all figures from external sources that were used in the original version of the presentation.
    All websites were accessed on 06/18/2020.

    \begin{itemize}
        \item Prism: Second figure in \url{https://de.wikipedia.org/wiki/Prisma_(Optik)}
        \item Gammasphere: \url{https://www.phy.anl.gov/gammasphere/}
        \item $^{229m}$Th: Figure 1 in L. von der Wense et al., Direct detection of the $^{229}$Th nuclear clock transition, Nature \textbf{533} (2016) 47-51 \url{https://doi.org/10.1038/nature17669}
        \item Resonance shape for a crystal: Figure 2 in W. E. Lamb, Capture of Neutrons by Atoms in a Crystal, Phys. Rev. \textbf{55} (1939) 190-197 \url{https://doi.org/10.1103/PhysRev.55.190}
        \item DHIPS: Figure 6.2 in C. Romig, Investigation of Nuclear Structure with Relative Self-Absorption Measurements, Dissertation, Technische Universit\"at Darmstadt (2015) \url{https://tuprints.ulb.tu-darmstadt.de/4446/}
        \item HI$\gamma$S: Figure 2 in H. R. Weller et al., Research opportunities at the upgraded HI$\gamma$S facility, Prog. Part. Nucl. Phys. \textbf{62} (2009) 257-303 \url{https://doi.org/10.1016/j.ppnp.2008.07.001}
        \item Spectrum: Modified from U. Friman-Gayer, Probing Nuclear Structure Relevant for Neutrinoless Double-Beta Decay with Nuclear Resonance Fluorescence, Dissertation, Technische Universit\"at Darmstadt (2020) \url{https://tuprints.ulb.tu-darmstadt.de/11385/}
        \item Schematic r-Process: Part (b) of Figure 5.75 in C. Iliadis, Nuclear Physics of Stars, Wiley-VCH (2015)
        \item Neutron star merger: \url{https://en.wikipedia.org/wiki/Neutron_star_merger}
        \item Isotope-selective scanning: \url{https://portal.slac.stanford.edu/sites/conf_public/facet_ii_wk_2015/Lists/Agenda1/Attachments/302/Hajima-NRF-NDA-FACET-II.pdf}
    \end{itemize}
\end{textblock}